Distributional Trees and Forests

### 2017-06-21 pkg/disttree/inst/useR2017/slides.Rnw
small touch-ups
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1470 255f4249-2263-4417-b1ea-8498779e27a7

\usepackage{Sweave} 
\usepackage{graphicx}
\setbeamertemplate{caption}{\insertcaption} 
\usetheme{Z}
%% includes a replacement for \usepackage{Sweave}
\usepackage{amsmath,tikz}
\usetikzlibrary{positioning,shapes,arrows,decorations.pathreplacing,calc,automata,mindmap}
\graphicspath{{plots/}}

@@

\begin{document}
\SweaveOpts{concordance=TRUE}

@@

\begin{frame}
\frametitle{Goals}
\vspace{1cm}
{\bf Tree:}
\begin{itemize}
  \item Specify the complete distribution in each subgroup.\\
  (location, scale and shape)
  \item Automatic detection of steps and abrupt changes. %(data driven)
  \item Capture non-linear and non-additive effects and interactions.
\end{itemize}
\vspace{0.5cm}
{\bf Forest:}
\begin{itemize}
  \item Smoother effects.
  \item Stabelization of the model.
\end{itemize}
\end{frame}

@@

<<tree, echo=FALSE, results=hide>>=
set.seed(7)
nobs <- 500
x <- runif(nobs, 0, 1)
mu <- sigma <- ytrue <- numeric(length = nobs)
for(i in 1:nobs) sigma[i] <- if(x[i]<=0.4) 1 else 3
for(i in 1:nobs) mu[i] <- if(x[i]<= 0.4|| x[i]>0.8) 4 else 12
y <- rnorm(nobs, mean = mu, sd = sigma)
#y <- rcnorm(nobs, mean = mu, sd = sigma, left = 0)
ytrue <- mu
data <- data.frame(cbind(y,x, ytrue))
tree <- disttree(y~x, data = data, family = NO(), type.tree = "mob")
#tree <- disttree(y~x, data = data, family = dist_list_cens_normal)

@@

\begin{frame}[fragile]
\frametitle{Fitting a Tree}
\begin{center}
\vspace*{-0.4cm}
Model: \code{disttree(y~x)}\\
\setkeys{Gin}{width=0.75\linewidth}
<<plottree_estpar, fig=TRUE, echo=FALSE>>=
pal <- rgb(c(0.97, 0.64, 1), c(0.70, 0.83, 1), c(0.30, 0.99, 1))
plot(tree, drop = TRUE, tnex = 1.5, #FUN = FUN,
     tp_args = list(fill = pal[c(1, 3)]), 
     ip_args = list(fill = pal[c(2, 3)]))
@
\end{center}
\end{frame}

@@

<<preliminaries3, echo=FALSE, results=hide>>=
load("~/svn/partykit/pkg/disttree/presentation/simlist20170621.rda")

>>>>

\setbeamertemplate{caption}{\insertcaption} 
\usetheme{Z}
%% includes a replacement for \usepackage{Sweave}
\usepackage{amsmath,tikz}
\usetikzlibrary{positioning,shapes,arrows,decorations.pathreplacing,calc,automata,mindmap}
\graphicspath{{plots/}}

@@

\begin{document}

@@

\begin{frame}
\frametitle{Goals}

\textbf{Distributional:} Specify the complete probability distribution
(including location, scale and shape).

\medskip

{\bf Tree:}
\begin{itemize}
  \item Automatic detection of steps and abrupt changes. %(data driven)
  \item Capture non-linear and non-additive effects and interactions.
\end{itemize}

\medskip

{\bf Forest:}
\begin{itemize}
  \item Smoother effects.
  \item Stabilization and regularization of the model.
\end{itemize}
\end{frame}

@@

<<tree, echo=FALSE, results=hide>>=
set.seed(7)
nobs <- 500
x <- runif(nobs, 0, 1)
mu <- sigma <- ytrue <- numeric(length = nobs)
for(i in 1:nobs) sigma[i] <- if(x[i]<=0.4) 1 else 3
for(i in 1:nobs) mu[i] <- if(x[i]<= 0.4|| x[i]>0.8) 4 else 12
y <- rnorm(nobs, mean = mu, sd = sigma)
#y <- rcnorm(nobs, mean = mu, sd = sigma, left = 0)
ytrue <- mu
data <- data.frame(cbind(y,x, ytrue))
tree <- disttree(y ~ x, data = data, family = NO(), type.tree = "mob")
#tree <- disttree(y ~ x, data = data, family = dist_list_cens_normal)

@@

\begin{frame}[fragile]
\frametitle{Fitting a Tree}
\begin{center}
\vspace*{-0.4cm}
Model: \code{disttree(y ~ x)}\\
\setkeys{Gin}{width=0.75\linewidth}
<<plottree_estpar, fig=TRUE, echo=FALSE>>=
pal <- rgb(c(0.97, 0.64, 1), c(0.70, 0.83, 1), c(0.30, 0.99, 1))
plot(tree, drop = TRUE, tnex = 1.5, #FUN = FUN,
     tp_args = list(fill = pal[c(1, 3)]), 
     ip_args = list(fill = pal[c(2, 3)]))
@
\end{center}
\end{frame}

@@

<<preliminaries3, echo=FALSE, results=hide>>=
load("simlist20170621.rda")
